A meta-analysis of powdery mildew yield loss mitigation strategies in Australian mungbean

### 2020-06-22 03_Prep_data.Rmd
Correct Let's/let's and all sentences on own line

First Let's get a list the of trials that reported LSD.

@@

## Reduce data set to required variables  
Let's tidy up the data set into a data frame of only the variables which are required for the analysis.

First remove the irrelevant columns/variables. Then calculate fungicide application timing variables relative to the first sign of disease. Entries with NA in the grain yield or powdery mildew severity are also removed from the data.

@@

Earlier we noted there were different doses of propiconazole which might influence our analysis. 
Let's check this by comparing a linear mixed effect model including and excluding dose. 
We already have a factor breaking down the dose in the `trial` variable, Let's make a new one without dose.

@@

Let's test the dose effect in a basic linear mixed effect model

@@

We may want to consider row spacing in the trials, However one of the locations has NA as the row spacing. 
For now Let's assign the most used row spacing of 0.33
```{r}
slimmer_PM_dat[is.na(slimmer_PM_dat$row_spacing),]
slimmer_PM_dat[is.na(slimmer_PM_dat$row_spacing),"row_spacing"] <- 0.33

>>>>

First let's get a list the of trials that reported LSD.

@@

## Reduce data set to required variables

Let's tidy up the data set into a data frame of only the variables which are required for the analysis.

First remove the irrelevant columns/variables.
Then calculate fungicide application timing variables relative to the first sign of disease.
Entries with `NA` in the grain yield or powdery mildew severity are also removed from the data.

@@

Earlier we noted there were different doses of propiconazole which might influence our analysis.
Let's check this by comparing a linear mixed effect model including and excluding dose.
We already have a factor breaking down the dose in the `trial` variable.
Let's make a new one without dose.

@@

Let's test the dose effect in a basic linear mixed effect model.

@@

We may want to consider row spacing in the trials, However one of the locations has NA as the row spacing. 
For now let's assign the most used row spacing of 0.33 m.

```{r}
slimmer_PM_dat[is.na(slimmer_PM_dat$row_spacing),]
slimmer_PM_dat[is.na(slimmer_PM_dat$row_spacing),"row_spacing"] <- 0.33
